An open library of human kinase domain constructs for automated bacterial expression

### 2016-02-02 manuscript/ms.tex
Added table and figure for results.

\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[mathbf,mathcal]{euler}
%\usepackage{citesort}
\usepackage[caption=false]{subfig}
\usepackage{dcolumn}
\usepackage{boxedminipage}
\usepackage{verbatim}
\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage[group-separator={,}]{siunitx}

@@

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[mathbf,mathcal]{euler}
%\usepackage{citesort}
\usepackage[caption=false]{subfig}
\usepackage{dcolumn}
\usepackage{boxedminipage}
\usepackage{verbatim}
\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage[group-separator={,}]{siunitx}
\usepackage{booktabs}

@@

\begin{table*}[]
\centering
\caption{Expression results by kinase}
\label{expression_results}
\footnotesize
\begin{tabular}{p{3.5cm}p{4cm}c}
\toprule
\bf{kinase expressed} & \bf{phosphatase co-expressed} & \bf{concentration ($ng/ \mu l$)} \\
\midrule
MK14\_HUMAN\_D0  & Lambda                    & 530                   \\
VRK3\_HUMAN\_D0  & Lambda                    & 506                   \\
GAK\_HUMAN\_D0   & Lambda                    & 485                   \\
CSK\_HUMAN\_D0   & Truncated YopH164         & 469                   \\
VRK1\_HUMAN\_D0  & Lambda                    & 467                   \\
KC1G3\_HUMAN\_D0 & Lambda                    & 422                   \\
FES\_HUMAN\_D0   & Truncated YopH164         & 330                   \\
PMYT1\_HUMAN\_D0 & Lambda                    & 285                   \\
MK03\_HUMAN\_D0  & Lambda                    & 273                   \\
STK3\_HUMAN\_D0  & Lambda                    & 257                   \\
DYR1A\_HUMAN\_D0 & Lambda                    & 256                   \\
KC1G1\_HUMAN\_D0 & Lambda                    & 256                   \\
MK11\_HUMAN\_D0  & Lambda                    & 238                   \\
MK13\_HUMAN\_D0  & Lambda                    & 238                   \\
EPHB1\_HUMAN\_D0 & Truncated YopH164         & 217                   \\
MK08\_HUMAN\_D0  & Lambda                    & 214                   \\
CDK16\_HUMAN\_D0 & Lambda                    & 202                   \\
EPHB2\_HUMAN\_D0 & Truncated YopH164         & 188                   \\
PAK4\_HUMAN\_D0  & Lambda                    & 179                   \\
CDKL1\_HUMAN\_D0 & Lambda                    & 174                   \\
SRC\_HUMAN\_D0   & Truncated YopH164         & 165                   \\
STK16\_HUMAN\_D0 & Lambda                    & 155                   \\
MAPK3\_HUMAN\_D0 & Lambda                    & 141                   \\
PAK6\_HUMAN\_D0  & Lambda                    & 135                   \\
CSK22\_HUMAN\_D0 & Lambda                    & 134                   \\
MERTK\_HUMAN\_D0 & Truncated YopH164         & 126                   \\
PAK7\_HUMAN\_D0  & Lambda                    & 110                   \\
CSK21\_HUMAN\_D0 & Lambda                    & 109                   \\
EPHA3\_HUMAN\_D0 & Truncated YopH164         & 106                   \\
BMPR2\_HUMAN\_D0 & Lambda                    & 106                   \\
M3K5\_HUMAN\_D0  & Lambda                    & 105                   \\
KCC2G\_HUMAN\_D0 & Lambda                    & 100                   \\
E2AK2\_HUMAN\_D0 & Lambda                    & 87                    \\
MK01\_HUMAN\_D0  & Lambda                    & 84                    \\
CSKP\_HUMAN\_D0  & Lambda                    & 76                    \\
CHK2\_HUMAN\_D0  & Lambda                    & 61                    \\
KC1G2\_HUMAN\_D0 & Lambda                    & 57                    \\
DMPK\_HUMAN\_D0  & Lambda                    & 57                    \\
KCC2B\_HUMAN\_D0 & Lambda                    & 53                    \\
FGFR1\_HUMAN\_D0 & Truncated YopH164         & 46                    \\
KS6A1\_HUMAN\_D1 & Lambda                    & 43                    \\
DAPK3\_HUMAN\_D0 & Lambda                    & 30                    \\
STK10\_HUMAN\_D0 & Lambda                    & 28                    \\
KC1D\_HUMAN\_D0  & Lambda                    & 28                    \\
KC1E\_HUMAN\_D0  & Lambda                    & 26                    \\
NEK1\_HUMAN\_D0  & Lambda                    & 25                    \\
CDK2\_HUMAN\_D0  & Lambda                    & 23                    \\
ABL1\_HUMAN\_D0  & Truncated YopH164         & 19                    \\
DAPK1\_HUMAN\_D0 & Lambda                    & 18                    \\
DYRK2\_HUMAN\_D0 & Lambda                    & 18                    \\
HASP\_HUMAN\_D0  & Lambda                    & 17                    \\
FGFR3\_HUMAN\_D0 & Truncated YopH164         & 17                    \\
EPHB3\_HUMAN\_D0 & Truncated YopH164         & 13                    \\
SLK\_HUMAN\_D0   & Lambda                    & 12                    \\
KCC2D\_HUMAN\_D0 & Lambda                    & 12                    \\
NEK7\_HUMAN\_D0  & Lambda                    & 10                    \\
PHKG2\_HUMAN\_D0 & Lambda                    & 10                    \\
VRK2\_HUMAN\_D0  & Lambda                    & 9                     \\
AAPK2\_HUMAN\_D0 & Lambda                    & 8                     \\
AURKA\_HUMAN\_D0 & Lambda                    & 8                     \\
MARK3\_HUMAN\_D0 & Lambda                    & 8                     \\
KAPCA\_HUMAN\_D0 & Lambda                    & 7                     \\
STK24\_HUMAN\_D0 & Lambda                    & 6                     \\
VGFR1\_HUMAN\_D0 & Truncated YopH164         & 4                     \\
KCC4\_HUMAN\_D0  & Lambda                    & 3                     \\
KCC1G\_HUMAN\_D0 & Lambda                    & 2                     \\
KCC2A\_HUMAN\_D0 & Lambda                    & 2                     \\
FAK2\_HUMAN\_D0  & Truncated YopH164         & 2                     \\             
\bottomrule
\end{tabular}
\end{table*}

\begin{figure}[tb]
   \includegraphics[width=\columnwidth]{kinome_expression.png}
  \caption{{\bf Representation of kinase domain expression results on phylogenetic tree.}
  Dark green circles represent kinases with expression above 250 $ng/ \mu l$.
  Light green circles represent kinases with expression between 100 and 250 $ng/ \mu l$.
  Yellow circles represent kinases with expression between 50 and 100 $ng/ \mu l$.
  Yellow circles represent kinases with any expression up to 50 $ng/ \mu l$.
  Image made with KinMap: \href{http://www.kinhub.org/kinmap}{http://www.kinhub.org/kinmap}. 
   }
  \label{fig:kinome_expression_tree}
\end{figure}
